% ====================================================================
% Harvard AGPS BibLaTeX Style
%
% Providing style, configuration, tests, and examples.
% Repository: https://github.com/harvardagps/HarvardAGPS
% ====================================================================
%% Copyright 2024 Gavin Kromhout
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either version 1.3
% of this license or (at your option) any later version.
% The latest version of this license is in
%   https://www.latex-project.org/lppl.txt
% and version 1.3c or later is part of all distributions of LaTeX
% version 2008 or later.
%
% This work has the LPPL maintenance status `maintained'.
% This work consists of all files listed in the repository.
% ====================================================================
% DISCLAIMER: This work is independent and has in no way been endorsed
%             by the University of Southern Queensland. This work is 
%             provided `as is' under the stated license.
% ====================================================================

% Load the document class and set the paper size and font size.
\documentclass[a4paper, 11pt]{article}

% Not using, here as an example only.
% \usepackage{harvard}
% \bibliographystyle{agsm}

% Not using, here as an example only.
% \usepackage{natbib}
% \usepackage{har2nat}
% \bibliographystyle{agsm}

% Use the BibLaTeX package for the citations and reference list.
% See the harvardagps.bbx and harvardagps.cbx style files for full details.
% IMPORTANT: The `biber' program must also be installed, perhaps additionally to LaTeX.
% IMPORTANT: BibLaTeX and `biber' must be version compatible with each other.
\usepackage[style=harvardagps]{biblatex}
\addbibresource{agps.bib}
% \addbibresource{biblatex-examples.bib}
% \addbibresource{xampl.bib}

% Make typography beautiful.
\usepackage{microtype}

% Remove unnecessary indentation.
\usepackage{noindentafter}
\NoIndentAfterEnv{itemize}
\NoIndentAfterEnv{enumerate}
\NoIndentAfterEnv{verbatim}

% Colour!
\usepackage[dvipsnames]{xcolor}

% Headers, footers, and page numbers.
\usepackage{pageslts}
\usepackage{fancyhdr}
% Redefine the plain page style.
% Notes:
% The first pages of commands like \chapter (book & report classes) call \thispagestyle{plain}.
% The first page of the article class does so too when \maketitle is used.
% The first page of table of contents and other indexes may do so too.
% In any case, a \pagestyle{plain} call is required to set the page style `from now on'.
\fancypagestyle{plain}{%
    \fancyhf{}% clear all header and footer fields
    \fancyfoot[C]{\thepage~of~\lastpageref*{LastPage}} % page of pages
    \renewcommand{\headrulewidth}{0pt}%
    \renewcommand{\footrulewidth}{0pt}%
}
\pagestyle{plain}

% Load these packages as late as possible and in this order,
% i.e. after most other packages.
\usepackage[hidelinks]{hyperref}
\urlstyle{same}
\usepackage{cleveref}

% Define commands.
\newcommand*{\repobaseurl}{https://github.com/harvardagps/HarvardAGPS}
\newcommand*{\BibTeX}{{\sc Bib}\TeX}
\newcommand*{\BibLaTeX}{Bib\LaTeX}
\newcommand*{\refNameNum}[1]{%
    \hyperref[#1]{\nameref*{#1}~\ref*{#1}}%
}
% These custom commands should not be needed in a typical paper.
% They assist with beginning and ending refsection to print a Reference per subsection. 
\newcommand*{\subsectionRefSection}[1]{
    \subsection{#1}
    \refsection
}
\newcommand*{\printsubbibliographyEndRefSection}{
    \printbibliography[heading=subbibliography, title=Reference]
    \endrefsection
}

% Define environments.
\newenvironment{agpsExample}{
    \setlength{\parindent}{0pt}
    \medskip
}
{}
\NoIndentAfterEnv{agpsExample}

\newenvironment{bareList}{%
    \begin{list}{}{}%
}
{\end{list}}

% Setup metadata.
\title{Harvard AGPS \BibLaTeX\ Style}
\author{Gavin Kromhout}
\date{2024/04/17 v1.1}

% Let's go.
\begin{document}

% Set page numbering scheme.
% May be used to switch numbering schemes throughout the document.
% Highly recommended after \begin{document} for the pageslts package.
\pagenumbering{arabic}

%%%%%%%%%%
\maketitle
%%%%%%%%%%

\begin{center}
    {\color{Magenta} \url{\repobaseurl}}
\end{center}

%%%%%%%%%%%%%%%%
\tableofcontents
%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%
\subsection{About}
%%%%%%%%%%%%%%%%%%

This repository presents a solution in \cref{subsec:Solution}, using \BibLaTeX, to the challenge of
citation and referencing in the Harvard AGPS style.

This repository exists because it was the most certain way that I could see to make a long list of
references exactly match the \emph{University of Southern Queensland Harvard AGPS Referencing Guide}
\autocite{UniSQ2020HarvarAGPSRefere}, henceforth The Guide. The aim is to fully and correctly
represent the citation and reference examples from the aforementioned referencing guide, and thus
validate and provide confidence that the configuration works correctly.

The long list of references, mentioned previously, came about due to selecting to write a
dissertation for my Bachelor of Engineering (Honours) degree that was of the \emph{literature review
    as a research methodology} type. Hence a large document with many references and it made sense to
use \LaTeX\ with \BibTeX\ (more on how that became \BibLaTeX\ is discussed in the alternatives
\namecref{subsec:Alternatives}, but I also needed a custom database for the literature search log
and \BibLaTeX\ also has that super power).

Finally, an internet search for a suitable Harvard AGPS bibliography / referencing style returned
only a few uncertain results, thus this effort may prove valuable to others.

%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Solution}
\label{subsec:Solution}
%%%%%%%%%%%%%%%%%%%%%%%

The solution presented here only requires three steps to apply and provides all of the required
configuration \emph{done} and validated by the examples in this document:

\begin{enumerate}
    \item set \texttt{biblatex} as the \emph{only} bibliography package in your .tex document, as
          shown below:
\begin{verbatim}
    \usepackage[style=harvardagps]{biblatex}
    \addbibresource{your.bib}
    ...
    \newpage
    \printbibliography[heading=bibintoc]
\end{verbatim}
    \item place copies of \texttt{harvardagps.bbx} and \texttt{harvardagps.cbx} files, from this
          repository, into the same directory as your .tex document.
    \item start writing see: \refNameNum{subsec:UsingAutociteAndTextcite}.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Disclaimer}
%%%%%%%%%%%%%%%%%%%%%%%

This work is independent and has in no way been endorsed by the University of Southern Queensland.
This work is provided `as is' under the stated license. The \texttt{agps.bib} file makes no claims
about being an accurate bibliographic database - it's aim is to exactly match The Guide.

%%%%%%%%%%%%%%%%%%%%
\subsection{License}
%%%%%%%%%%%%%%%%%%%%

\begin{small}
\begin{verbatim}
Copyright 2024 Gavin Kromhout

This work may be distributed and/or modified under the
conditions of the LaTeX Project Public License, either version 1.3
of this license or (at your option) any later version.
The latest version of this license is in
https://www.latex-project.org/lppl.txt
and version 1.3c or later is part of all distributions of LaTeX
version 2008 or later.

This work has the LPPL maintenance status `maintained'.
This work consists of all files listed in the repository.
\end{verbatim}
\end{small}

%%%%%%%%%%%%%%%%%%%
\subsection{Issues}
%%%%%%%%%%%%%%%%%%%

For any issues:

\begin{enumerate}
\item browse the source files in this repository - these files show complete examples with extensive comments;
\item seek answers on the internet (of course);
\item raise an issue against the GitHub repository, ideally with a minimal working example (MWE)
that others can contribute to, and perhaps even include a suggested fix.
\end{enumerate}

Note well that any settings in a \texttt{biblatex.cfg} file will override the style settings.

\medskip
\noindent
For reference, testing and implementation of this solution was performed with texlive (Debian)
version: 2022.20230122-3; pdfTeX version: 3.141592653-2.6-1.40.24; \BibLaTeX\ version: v3.18b, and
\texttt{biber} version: 2.18.

According to the \texttt{biblatex} package manual \autocite[8]{KimeEtAl2022biblatPackag},
\BibLaTeX\ version: 3.18 is compatible with \texttt{biber} version: 2.18.

%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Alternatives}
\label{subsec:Alternatives}
%%%%%%%%%%%%%%%%%%%%%%%%%%%

If all that is required is a working author-year referencing style, or if AGSM is specifically
required, then consider the \texttt{harvard} package and the \texttt{agsm} style:

\begin{verbatim}
    \usepackage{harvard}
    \bibliographystyle{agsm}
\end{verbatim}

Should the limitations of the above become unacceptable, or perhaps a suitable \texttt{natbib} style
is immediately available, or the wide support of journals is required, then consider the
\texttt{natbib} package and friends:

\begin{verbatim}
    \usepackage{natbib}
    \usepackage{har2nat}
    \bibliographystyle{agsm}
\end{verbatim}

Note also that if the document already contains \texttt{natbib} citation commands, and those
commands should be preserved, for example to be able to easily switch back and forth, then
\texttt{biblatex} load-time option \texttt{natbib=true} \emph{might} be useful to try the solution
presented in this repository (not tested, contributions welcome).

Finally, the above alternatives still require significant configuration and possibly the creation of
a custom .bst style file to approach the Harvard AGPS referencing style, in fact that was initially
the intent for this repository, instead for the greatest configurability consider \BibLaTeX\ as has
been done in the solution presented here.

%%%%%%%%%%%%%%%%%%
\newpage
\section{Examples}
%%%%%%%%%%%%%%%%%%

The aim of the Harvard AGPS \BibLaTeX\ Style is to exactly match the examples found in the
\emph{University of Southern Queensland Harvard AGPS Referencing Guide}
\autocite{UniSQ2020HarvarAGPSRefere}, henceforth The Guide.

Note carefully that these examples are not a copy and paste from The Guide, they are completely
generated from the \texttt{agps.bib} entries using the style files.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsectionRefSection{Using \texttt{autocite} and \texttt{textcite}}
\label{subsec:UsingAutociteAndTextcite}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Using \verb|\autocite| and \verb|\textcite| as the base commands is the recommended approach for
citation in a typical paper.

\begin{agpsExample}

    Example using \verb|\autocite{Smith1985MicroePolicyFramew}|:

    \begin{bareList}
        \item \ldots\ \autocite{Smith1985MicroePolicyFramew}.
    \end{bareList}

    Example using \verb|\autocite[65]{Smith1985MicroePolicyFramew}|:

    \begin{bareList}
        \item \ldots\ \autocite[65]{Smith1985MicroePolicyFramew}.
    \end{bareList}

    Example using \verb|\textcite{Smith1985MicroePolicyFramew}|:

    \begin{bareList}
        \item \textcite{Smith1985MicroePolicyFramew} \ldots
    \end{bareList}

    Example using \verb|\textcite[65-66]{Smith1985MicroePolicyFramew}|:

    \begin{bareList}
        \item \textcite[65-66]{Smith1985MicroePolicyFramew} \ldots
    \end{bareList}

\end{agpsExample}

\printsubbibliographyEndRefSection

\subsubsection{Reasoning}

The reasoning for recommending this approach is, firstly, that the combination of \verb|\autocite|
and \verb|\textcite| seem to be the most likely to just work and do the right thing when changing
\BibLaTeX\ styles.

In the Harvard \BibLaTeX\ AGPS Style \verb|\autocite| is already configured to use \verb|\parencite|
so there is no need to use it directly and the former has the added advantage of being considered to
be a style-independent command which is able to automatically switch styles whereas the latter
should always be expected to wrap the whole citation in parentheses or square brackets, which may
not be the right outcome for all referencing styles.

Secondly, when switching to a completely different bibliography package, then \verb|\autocite|
should be able to be replaced with the base citation command from that package with predictable
results, and \verb|\textcite| can be replaced with the text/noun/subject equivalent from that
package to provide the required outcome.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{(Not) Using \texttt{cite}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This is a validation example only and \emph{not} recommended for creating citations in a typical
paper. The \verb|\cite| command is described as a bare command by the \texttt{biblatex} package
manual \autocite[110]{KimeEtAl2022biblatPackag} and the Harvard \BibLaTeX\ AGPS style makes no
attempt to change that. The bare output does \emph{not} provide a valid Harvard AGPS citation.

\refsection

\begin{agpsExample}

    Example using \verb|\cite|:

    \begin{bareList}
        \item \cite{Smith1985MicroePolicyFramew}
    \end{bareList}

\end{agpsExample}

\printsubbibliographyEndRefSection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsectionRefSection{(Not) Using \texttt{fullcite}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This is a validation example only and \emph{not} recommended for creating citations in a typical
paper. Note that the full reference (aka full citation) is printed, at the citation location, using
the reference list formatting, except in-text. This output does \emph{not} provide a valid Harvard
AGPS in-text citation.

\begin{agpsExample}

    Example using \verb|\fullcite|:

    \begin{bareList}
        \item \fullcite{Smith1985MicroePolicyFramew} $\leftarrow$ no period as text is in-line.
    \end{bareList}

\end{agpsExample}

\printsubbibliographyEndRefSection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsectionRefSection{No Address}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

An example for which the address is not clear in print materials. This example is `as seen' in The
Guide. Since The Guide encourages terseness, on occasion, for the publisher address this style does
not automatically insert the required \texttt{n.p.}\ abbreviation for `no place' in the reference
list. This may be performed manually, where required, in the \texttt{.bib} file by setting
\verb|Address = {n.p.}| on the entry.

\begin{agpsExample}

    Example:

    \begin{bareList}
        \item \ldots\ \autocite{SnooksCo2002StyleManualAuthor}.
    \end{bareList}

\end{agpsExample}

\printsubbibliographyEndRefSection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsectionRefSection{Single Author}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This is a single author book example. Note how The Guide encourages being terse with the publisher
address because it is already clear from the other details. Note also how a list of pages is
specified and the plural for pages \texttt{pp.}\ is automatically inserted.

\begin{agpsExample}

    Example using \verb|\autocite[23,25]{Abbott2008CambriIntrodNarrat}|:

    \begin{bareList}
        \item \ldots\ \autocite[23,25]{Abbott2008CambriIntrodNarrat}.
    \end{bareList}

    Example using \verb|\textcite[23,25]{Abbott2008CambriIntrodNarrat}|:

    \begin{bareList}
        \item \textcite[23,25]{Abbott2008CambriIntrodNarrat} \ldots
    \end{bareList}

\end{agpsExample}

\printsubbibliographyEndRefSection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsectionRefSection{Two or Three Authors}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{agpsExample}

    Examples:

    \begin{bareList}
        \item \ldots\ \autocite[80]{KakadiaEtAl2004NetworConcepTechno}.
        \item \textcite{KakadiaEtAl2004NetworConcepTechno} \ldots
        \item \ldots\ \autocite{DouglasEtAl2009CitizeEngineHandbo}.
        \item \textcite[11]{DouglasEtAl2009CitizeEngineHandbo} \ldots
    \end{bareList}

\end{agpsExample}

\printsubbibliographyEndRefSection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsectionRefSection{More Than Three Authors}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{agpsExample}

    Examples:

    \begin{bareList}
        \item \ldots\ \autocite[54]{BeerEtAl2012ManagePublicServic} \ldots
        \item \textcite[54]{BeerEtAl2012ManagePublicServic} \ldots
    \end{bareList}

\end{agpsExample}

\printsubbibliographyEndRefSection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsectionRefSection{Unknown Author}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{agpsExample}

    Examples:

    \begin{bareList}
        \item \ldots\ \autocite[21-2]{StageAcquitBeing1996}.
        \item \ldots\ \textcite[21-2]{StageAcquitBeing1996}.
    \end{bareList}

\end{agpsExample}

\printsubbibliographyEndRefSection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsectionRefSection{Corporate (Group) Author}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{agpsExample}

    Examples:

    \begin{bareList}
        \item \ldots\ \textcite[2-3]{UrapunLandClaim2001} \ldots
        \item \ldots\ \autocite[2-3]{UrapunLandClaim2001}.
        \item \textcite[9]{PCSC1983QueensPlanniCommit} \ldots
        \item \ldots\ \autocite[9]{PCSC1983QueensPlanniCommit}.
        \item \autocite{OfficeoftheAboriginalLandCommissioner2001UrapunLandClaim}
    \end{bareList}

\end{agpsExample}

\printsubbibliographyEndRefSection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsectionRefSection{Multiple Works by Same Author}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The author name(s) of multiple works by exactly the same author(s) are replaced with 2 em-dashes in
the reference list and the style is therefore able to automatically match The Guide exactly in this
respect.  However, it would appear that repeated author name(s) when the overall work authorship is
different (further/multiple authors are involved that differ from the previously listed work) are
not so easily replaced with the current version of \BibLaTeX\ without resorting to high risk code in
what needs to be a stable style. An automatic solution may need to wait for core \BibLaTeX\ support
and/or more thorough testing. A manual workaround is possible as shown in the \texttt{agps.bib} file
and the \texttt{ChaffeeEtAl2002CriticThinkiThough} entry using the \texttt{SortName},
\texttt{ShortAuthor} field and a sprinkle of \LaTeX\ in the \texttt{Author} field to achieve an
exact match to The Guide.

\begin{agpsExample}

    Examples:

    \begin{bareList}
        \item \ldots\ \autocite[215]{LyonEtAl2002Circus}.
        \item \ldots\ \autocite[27]{LyonEtAl2002Clowns}.
        \item \ldots\ \autocites[215]{LyonEtAl2002Circus}[27]{LyonEtAl2002Clowns}[19]{LyonEtAl2008NoFurtheInform}.
        \item \textcites[215]{LyonEtAl2002Circus}[27]{LyonEtAl2002Clowns}[19]{LyonEtAl2008NoFurtheInform} \ldots
        \item \ldots\ \autocite{ChaffeeEtAl2002CriticThinkiThough}.
        \item \textcite{ChaffeeEtAl2002CriticThinkiThough} \ldots
        \item \ldots \autocite{Chaffee1998ThinkeWay8, ChaffeeEtAl2002CriticThinkiThough, Chaffee1991ThinkiCritic}.
    \end{bareList}

\end{agpsExample}

\nocite{Chaffee1991ThinkiCritic, Chaffee1998ThinkeWay8, ChaffeeEtAl2002CriticThinkiThough}%

\printsubbibliographyEndRefSection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsectionRefSection{Different Authors with Same Surname}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{agpsExample}

    Examples:

    \begin{bareList}
        \item \ldots\ \textcite[12]{Smith1981TheoryMicroePolicy} \ldots\
        \autocite[65]{Smith1985MicroePolicyFramew}.
    \end{bareList}

\end{agpsExample}

\printsubbibliographyEndRefSection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsectionRefSection{Edited Book/Collection}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{agpsExample}

    Examples:

    \begin{bareList}
        \item \ldots\ \autocite[ed.][27]{Brofenbrenner2005MakingHumanBeings}.
        \item \ldots\ edited by \autocite[27]{Brofenbrenner2005MakingHumanBeings}.
    \end{bareList}

\end{agpsExample}

\printsubbibliographyEndRefSection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsectionRefSection{Authors Citing Other Authors (Secondary Citation)}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{agpsExample}

    Examples:

    \begin{bareList}
        \item Brown \autocite[cited in][99]{Smith1995FoodProcesTechno} \ldots
        \item \ldots\ \autocite[Brown, cited in][99]{Smith1995FoodProcesTechno}.
    \end{bareList}

\end{agpsExample}

\printsubbibliographyEndRefSection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsectionRefSection{No Publication Date}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{agpsExample}

    Examples:

    \begin{bareList}
        \item \ldots \autocite{CreativeCommonsNdShareYourWork}.
        \item \citeauthor{LloydWebber1970JesusCSupers}'s \autocite*{LloydWebber1970JesusCSupers} \ldots
        \item \textcite{LloydWebber1970JesusCSupers} \ldots
        \item \ldots\ \autocite{LloydWebber1970JesusCSupers}
    \end{bareList}

\end{agpsExample}

\printsubbibliographyEndRefSection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsectionRefSection{Editions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{agpsExample}

    Examples:

    \begin{bareList}
        \item \ldots\ \autocite[12]{Abbott2008CambriIntrodNarrat}.
        \item \autocite[12]{Abbott2008CambriIntrodNarrat} \ldots
    \end{bareList}

\end{agpsExample}

\printsubbibliographyEndRefSection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsectionRefSection{Titles}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{agpsExample}

    Example:

    \begin{bareList}
        \item \ldots\ \autocite[214-218]{Reichard2016DeadloDisillAmeric}.
    \end{bareList}

\end{agpsExample}

\printsubbibliographyEndRefSection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsectionRefSection{URLs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{agpsExample}

    Examples:

    \begin{bareList}
        \item \ldots\ \autocite{TheBodyShopAustralia2018BodyShopAustra}.
        \item \ldots\ \citeauthor{TheBodyShopAustralia2018BodyShopAustra}
        website \textless\citeurl{TheBodyShopAustralia2018BodyShopAustra}\textgreater.
    \end{bareList}

\end{agpsExample}

\printsubbibliographyEndRefSection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsectionRefSection{Books}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{agpsExample}

    Examples:

    \begin{bareList}
        \item \Textcite[11]{DouglasEtAl2009CitizeEngineHandbo} \ldots
        \item \ldots \autocite[27]{McClainEtAl1999SchaumQuickGuide}.
        \item \ldots \autocite[36]{Ware2010CottagbySea}.
    \end{bareList}

\end{agpsExample}

\printsubbibliographyEndRefSection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsectionRefSection{Chapter in Edited Books, Including Dictionaries and Encyclopedias}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{agpsExample}

    Examples:

    \begin{bareList}
        \item \ldots \autocite[255]{Brandt2002DefectNewborMorali}.
        \item \ldots \autocite[26]{Gould2000MoreThingsHeaven}.
        \item \ldots \autocite[5]{DaddsEtAl2004DiagnoIssues}.
        \item \Textcite[334]{ConcisOxfordDictio1990} $\leftarrow$ using the \texttt{skipbib} option
        in the entry prevents the entry from appearing in the reference list.
    \end{bareList}

\end{agpsExample}

\printsubbibliographyEndRefSection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsectionRefSection{Journal Articles, Newspaper Articles, Magazine Articles}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{agpsExample}

    Examples:

    \begin{bareList}
        \item \Citeauthor{Wong2009RethinHobbitIndone}'s \citeyear{Wong2009RethinHobbitIndone}
        \ldots\ \pnotecite[67-69]{Wong2009RethinHobbitIndone}.
        \item \ldots\ \autocite[23-5]{Griffith1995CoordiFamilySchool}.
        \item \ldots\ \autocite[23-5]{McCarthyEtAl2021DroneThermaRemote}.
        \item \ldots\ \autocite[16-17]{JeffersEtAl2010RealitDrough}.
        \item \ldots\ (\citetitle{WeekenAustra1987} 24-25 Jan. \citeyear[19]{WeekenAustra1987})
        $\leftarrow$ using the \texttt{skipbib} option in the entry prevents the entry from
        appearing in the reference list.
        \item \Textcite{ClearyEtAl2001ItsEndLong} \ldots
    \end{bareList}

\end{agpsExample}

\printsubbibliographyEndRefSection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsectionRefSection{Website Home Page}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{agpsExample}

    Examples:

    \begin{bareList}
        \item \ldots\ \textless\url{www.usq.edu.au}\textgreater.
        \item \ldots\ \autocite{USQ2019UniverSoutheQueens}.
    \end{bareList}

\end{agpsExample}

\printsubbibliographyEndRefSection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsectionRefSection{Web Page}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{agpsExample}

    Example:

    \begin{bareList}
        \item \ldots\ \autocite{TheBodyShopAustralia2018CorporSocialRespon}.
    \end{bareList}

\end{agpsExample}

\printsubbibliographyEndRefSection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsectionRefSection{Web Document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{agpsExample}

    Example:

    \begin{bareList}
        \item \ldots\ \autocite{Anderson2000CASAApprovAvgas}.
    \end{bareList}

\end{agpsExample}

\printsubbibliographyEndRefSection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsectionRefSection{Published Papers}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{agpsExample}

    Examples:

    \begin{bareList}
        \item \ldots\ \autocite[24]{Smith1996AcademOrientProgra}.
        \item \Textcite[24]{Smith1996AcademOrientProgra} \ldots
    \end{bareList}

\end{agpsExample}

\printsubbibliographyEndRefSection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsectionRefSection{Unpublished Papers}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{agpsExample}

    Example:

    \begin{bareList}
        \item \ldots\ \autocite{Pomfret2001EconomDiversNew}.
    \end{bareList}

\end{agpsExample}

\printsubbibliographyEndRefSection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsectionRefSection{Your Own Previous Assignment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{agpsExample}

    Example:

    \begin{bareList}
        \item \Textcite[45]{Smith2018Assign1} \ldots
    \end{bareList}

\end{agpsExample}

\printsubbibliographyEndRefSection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Reference vs References}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This style manual and test document (agps.tex) prints a Reference in each subsection to provide the
examples. The \texttt{refsection} commands are used to effectively hide the citations from the
actual reference list by placing them into a reference segment. \underline{Typically don't use this
method in a paper}.

Note carefully that, in the examples, this document is not citing anything from the example sources,
merely providing citation and reference examples.

Where citation and referencing is required, this document includes the required in-text citation and
the full citation is listed in the single References section at the end of the paper as typically
required by the Harvard AGPS style.

%%%%%%%%%%%% References %%%%%%%%%%%%
\newpage
\printbibliography[heading=bibintoc]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% The End.
\end{document}
